Invasive lionfish present region-wide variation of allometric growth in the Western Atlantic

### 2018-05-24 docs/Manuscript.Rmd
Close #4 : Added to the discussion

A new pair of allometric growth parameters for lionfish in the central Mexican Caribbean are provided, complimenting existing literature for other sites in the Mexican Caribbean \citep{sabidoitza_2016,sabidoitz_2016}. Additionally, the study identifies regional differences in length-weight relationships.

@@

There are evident differences in weight-at-length between organisms from the Caribbean and Gulf of Mexico / North-Western Atlantic. Weight estimates with parameters from the Gulf of Mexico and North-Western Atlantic tend to be higher than those from the Caribbean. Similar regional variation has been reported for age-at-length relationships of this species across the invaded region \citep{fogg_2015,edwards_2014}, or when comparing populations from the invasion and native ranges \citep{pusack_2016}. These may be driven by genetic differences or organisms being exposed to distinct environmental conditions. For example, work on mitochondrial DNA has shown two distinct population groups, identified as the "Caribbean group" and "Northern Group" \citep{betancurr_2011}. Alternatively, \citet{fogg_2015} suggest that differences observed in age-at-length "may bemore related to climate rather than other biological and ecological factors". Differences in weight-at-length could also reflect differences in energy input (*i.e.* in some regions, lionfish eat more) or differential usage of this energy (*e.g.* regional differences in predator abundances lead to different usage of energy), or a combination of both. Future research should focus on identifying which occurs here.

>>>>

<!-- A new pair of allometric growth parameters for lionfish in the central Mexican Caribbean are provided, complimenting existing literature for other sites in the Mexican Caribbean \citep{sabidoitza_2016,sabidoitz_2016}. Additionally, the study identifies regional differences in length-weight relationships. -->

@@

There are evident differences in weight-at-length between organisms from the Caribbean and Gulf of Mexico / North-Western Atlantic. Weight estimates with parameters from the Gulf of Mexico and North-Western Atlantic tend to be higher than those from the Caribbean. Similar regional variation has been reported for age-at-length relationships of this species across the invaded region \citep{fogg_2015,edwards_2014}, or when comparing populations from the invasion and native ranges \citep{pusack_2016}. These may be driven by genetic differences or organisms being exposed to distinct environmental conditions. For example, work on mitochondrial DNA has shown two distinct population groups, identified as the "Caribbean group" and "Northern Group" \citep{betancurr_2011}. Alternatively, \citet{fogg_2015} suggest that differences observed in age-at-length may be driven by climate, and not by ecological processes. Differences in weight-at-length could also reflect differences in energy input (*i.e.* in some regions, lionfish eat more) or differential usage of this energy (*e.g.* regional differences in predator abundances lead to different usage of energy), or a combination of both. Future research should focus on identifying which occurs here.

Differences in length-weight relationships have traditionally been highlighted as potential pitfalls to fishery management. For example, \citet{wilson_2012} shows that small-scale variations in other Scorpaeniformes (*Sebastes rastrelliger*) translate to differential landings, effort, and catch per unit effort in the live fish fishery of California, and that these differences must be taken into account in management plans. The lionfish case poses the opposite scenario, where the manager desires to erradicate species. To accurately estimate lionfish removal efforts and allocate resources to manage the invasion, we must aknowledge and understand the regional biological differences.

### 2018-05-24 docs/Manuscript.tex
Close #4 : Added to the discussion

The main objective of this work was to compare allometric growth of
lionfish throughout their invasion range. Allometric parameters were
retreived from scientific literature, and an additional pair of
parameters was calculated from filed observations in the central Mexican
Caribbean.

Length-weight relationships (n = 17) identified in literature were
obtained for the North Atlantic (n = 1), Gulf of Mexico (n = 7,), and
Caribbean (n = 10). Information on sampling methods, sex
differentiation, location, and depth ranges of each study was retrieved
when available. Studies were assumed to include both genders if gender
was unspecified. Locations where allometric studies have been performed
are shown in Figure \ref{fig:map} and Table \ref{tab:all_params}.

Studies inconsistently defined \(a\) as either the ponderal index from
Eq. \ref{eq:allometric} or the y-intercept (\(c\)) from Eq.
\ref{eq:log-alo-trans}. Other studies incorrectly reported parameters as
mm-to-g conversions when they were in fact cm-to-g conversions. Here,
all parameters are reported as TL(mm) to TW(gr) conversions. When
required, values from other studies were transformed for consistency.

@@

Combining the length-weight parameters extracted from the literature and
the additional pair calculated here, we obtain a total of 18 pairs. We
test wether using \emph{ex situ} parameters produces differences in
weight estimates by estimating TW from the 109 length observations of
lionfish from the central Mexican Caribbean with each ot the 18
relationships. Predicted weights were divided by know observed weights
to obtain a simple measurement of over- or underestimation. Difference
in mean weight ratios across studies were tested with a one-way analysis
of variance (ANOVA). All analyses were performed in R version 3.5.0
\citep{rcore_2018}. Raw data and code used in this work are available at
dryad.org.

@@

A new pair of allometric growth parameters for lionfish in the central
Mexican Caribbean are provided, complimenting existing literature for
other sites in the Mexican Caribbean
\citep{sabidoitza_2016,sabidoitz_2016}. Additionally, the study
identifies regional differences in length-weight relationships.

@@

There are evident differences in weight-at-length between organisms from
the Caribbean and Gulf of Mexico / North-Western Atlantic. Weight
estimates with parameters from the Gulf of Mexico and North-Western
Atlantic tend to be higher than those from the Caribbean. Similar
regional variation has been reported for age-at-length relationships of
this species across the invaded region \citep{fogg_2015,edwards_2014},
or when comparing populations from the invasion and native ranges
\citep{pusack_2016}. These may be driven by genetic differences or
organisms being exposed to distinct environmental conditions. For
example, work on mitochondrial DNA has shown two distinct population
groups, identified as the ``Caribbean group'' and ``Northern Group''
\citep{betancurr_2011}. Alternatively, \citet{fogg_2015} suggest that
differences observed in age-at-length ``may bemore related to climate
rather than other biological and ecological factors''. Differences in
weight-at-length could also reflect differences in energy input
(\emph{i.e.} in some regions, lionfish eat more) or differential usage
of this energy (\emph{e.g.} regional differences in predator abundances
lead to different usage of energy), or a combination of both. Future
research should focus on identifying which occurs here.

>>>>

The main objective of this work was to compare allometric growth of
lionfish throughout their invasion range. Allometric parameters were
retreived from scientific literature, and an additional pair of
parameters were calculated from filed observations in the central
Mexican Caribbean.

Length-weight relationships (n = 17) identified in literature were
obtained for the North Atlantic (n = 1), Gulf of Mexico (n = 7,), and
Caribbean (n = 10). Information on sampling methods, sex
differentiation, location, and depth ranges of each study was retrieved
when available. Studies were assumed to include both genders if gender
was unspecified. Studies inconsistently defined \(a\) as either the
ponderal index from Eq. \ref{eq:allometric} or the y-intercept (\(c\))
from Eq. \ref{eq:log-alo-trans}. Other studies incorrectly reported
parameters as mm-to-g conversions when they were in fact cm-to-g
conversions. Here, all parameters are reported as TL(mm) to TW(gr)
conversions. When required, values from other studies were transformed
for consistency. Locations where allometric studies have been performed
are shown in Figure \ref{fig:map} and Table \ref{tab:all_params}.

@@

Combining the length-weight parameters extracted from the literature and
the additional pair calculated here, we obtain a total of 18 pairs. We
test wether using \emph{ex situ} parameters produces differences in
weight estimates by estimating TW for the 109 length observations of
lionfish from the central Mexican Caribbean with each of the 18
relationships. Predicted weights were divided by know observed weights
to obtain a simple measurement of over- or underestimation. Difference
in mean weight ratios across studies were tested with a one-way analysis
of variance (ANOVA). All analyses were performed in R version 3.5.0
\citep{rcore_2018}. Raw data and code used in this work are available at
dryad.org.

@@

@@

There are evident differences in weight-at-length between organisms from
the Caribbean and Gulf of Mexico / North-Western Atlantic. Weight
estimates with parameters from the Gulf of Mexico and North-Western
Atlantic tend to be higher than those from the Caribbean. Similar
regional variation has been reported for age-at-length relationships of
this species across the invaded region \citep{fogg_2015,edwards_2014},
or when comparing populations from the invasion and native ranges
\citep{pusack_2016}. These may be driven by genetic differences or
organisms being exposed to distinct environmental conditions. For
example, work on mitochondrial DNA has shown two distinct population
groups, identified as the ``Caribbean group'' and ``Northern Group''
\citep{betancurr_2011}. Alternatively, \citet{fogg_2015} suggest that
differences observed in age-at-length may be driven by climate, and not
by ecological processes. Differences in weight-at-length could also
reflect differences in energy input (\emph{i.e.} in some regions,
lionfish eat more) or differential usage of this energy (\emph{e.g.}
regional differences in predator abundances lead to different usage of
energy), or a combination of both. Future research should focus on
identifying which occurs here.

Differences in length-weight relationships have traditionally been
highlighted as potential pitfalls to fishery management. For example,
\citet{wilson_2012} shows that small-scale variations in other
Scorpaeniformes (\emph{Sebastes rastrelliger}) translate to differential
landings, effort, and catch per unit effort in the live fish fishery of
California, and that these differences must be taken into account in
management plans. The lionfish case poses the opposite scenario, where
the manager desires to erradicate species. To accurately estimate
lionfish removal efforts and allocate resources to manage the invasion,
we must aknowledge and understand the regional biological differences.
